---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->

# DataFEWSionR

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

## Who are we?
We are an interdisciplinary group of graduate students from Iowa State University.
Part of our mission is to form collaborative environments to engage in cross-cutting 
research projects.

We have developed a shiny application using a variety of data relevant to Iowans broadly
and incorporated all of the data in a user friendly interface. We created this as we 
felt there was a need to have better access to these data and in a way that is clear for the user.

Iowa has approximately _____ of people, and they are dispursed throughout the state, with heavy population centers in 
Des Moines, Cedar Rapids, and Iowa City. The remaining population exists in rural areas where a significant amount of the 
agricultural crops are grown. 

As climate change makes weather events more uncertain and the severity of droughts and extreme weather events forecast to increase
in the near and long term, we incorporated the most recent climate change models with the perception of individuals on 
climate change. This shows that the regions that are most likely to be impacted by climate change are those in rural areas.

## How can you use our Shiny Application?

First, you will need to install R and RStudio. See the links to download R and RStudio, respectively.

You will then need a few packages install and loaded into RStudio.

```{r, eval = FALSE}
library(devtools)
library(leaflet)
library(shiny)
library(sf)
library(tidyverse)
```

Now you are ready to download our package, `DataFEWSionR`. 

```{r, eval = FALSE}

devtools::install_github("loganjohnson0/DataFEWSionR")

library(DataFEWSionR)
```

Now if there are no errors or warnings, you should be ready to go! <b> GREAT! </b>




